\chapter{Homogeneous Equations}
A linear $n$-th order differential equation is \textbf{homogeneous} if it takes a form of
\begin{equation*}
	H(x,y) = a_n(x)\frac{\mathrm{d}^ny}{\mathrm{d}x^n} + a_{n-1}(x)\frac{\mathrm{d}^{n-1}y}{\mathrm{d}x^{n-1}} + ... + a_1(x)\frac{\mathrm{d}y}{\mathrm{d}x} + a_0(x)y = 0
\end{equation*}
A \textbf{non-homogeneous} equation is 
\begin{equation*}
	H(x,y) = g(x)
\end{equation*}
on a interval where $g(x) \neq 0$. It will be shown that an associated homogeneous equation will need to be solved first before we can solve the non-homogeneous equation. We will make two simple assumptions, one the coefficient functions and $g(x)$ are continuous. The second that $a_n(x) \neq 0$ for all $x$ in a common interval $I$. 
\section{Notational Differential Operators}
A differential operator is a operator that turns a differentiable function into a function. That sounds exactly like what we do with the regular differential operator, and the point is that this is the regular differential operator. We let the differential operator $D$ be exactly that.  
\begin{equation*}
	D^n\{f(x)\} = f'(x) = \dd{f(x)}{x}
\end{equation*}
The properties of differentiation imposes two useful rules. The first is the ability to factor out a constant coefficient outside of the operator.  
\begin{equation*}
	cD^n\{f(x)\} = D^n\{c\times f(x)\}
\end{equation*}
The second is the sum and difference rule, 
\begin{equation*}
	D^n\{ f(x) \pm g(x) \} = D^n\{f(x)\} \pm D^n\{g(x)\}
\end{equation*}
These two rules allows us to write the homogeneous expression in terms of a polynomial differential operator. 
\begin{equation*}
	\mathrm{L} = a_n(x)D^n + a_{n-1}(x)D^{n-1} + ... + a_1D + a_0(x)
\end{equation*}
\pagebreak
\section{Superposition Principle}
The sum or superposition of two or more solutions to a homogeneous linear differential equation is also consider to be a solution to a differential equation. This is an interesting concept because it actual limits to the amount of useful solutions we want. Consider that we could super impose solutions that were just multiple factors of each other. That doesn't do much for us, so we could instead super impose just two solutions who are linearly independent of each other.

But let's just consider the simple case, where $\gamma_1, \gamma_2,\gamma_3, ... ,\gamma_n$ are considered to be solutions to a differential equation on some common interval $I$. The linear combination 
\begin{equation*}
	y= c_1\gamma_1 + c_2\gamma_2 + c_3\gamma_3 + ... + c_n\gamma_n
\end{equation*} 
is considered to be a solution with $c_1 ... c_n$ are considered to be arbitrary constants. We can compactly write this as 
\begin{equation*}
	y = \sum_{i=0}^k c_i \gamma_i(x)
\end{equation*}
\subsection{Proof of Principle}
A good way to test the usage of our $\mr{L}$ is using it to prove the superposition principle. Consider the case $k=2$, we let $\mr{L}$ be a polynomial differential operator and let $\gamma_1$,$\gamma_2$ be solutions to the differential equation, expressed in $\mr{L}$,
\begin{equation*}
	\mr{L}\{y\}= 0
\end{equation*}
We define $c_1\gamma_1 + c_2\gamma_2 = y$ and by linearity, 
\begin{align*}
	\mr{L}\{ c_1\gamma_1 + c_2\gamma_2 \} &= \mr{L}\{ y \} = 0 \\ 
	 c_1\mr{L}\{\gamma_1\}+ c_2\mr{L}\{\gamma_2\} &= 0 \\ 
	 c_1 \times 0 + c_2 \times 0 &= 0   
\end{align*}
Since $\gamma_1$ and $\gamma_2$ are known solutions to $\mr{L}\{y\} = 0$, we know that they evaluate to zero. There by proving our superposition principle. 

\section{Solutions of Differential Equations}
We are interested in linearly independent solutions. Note the superposition principle allows us to super impose any solution we have with independent solutions. To determine if a set of solutions are linearly independent, we take the Worskin Detriment,

\begin{equation*}
	\mathbf{W} = \begin{bmatrix}
	    f_1 && f_2  && f_3 \\ 
	    f'_1 && f'_2  && f'_3 \\ 
	    f''_1 && f''_2  && f''_3 \\ 
	\end{bmatrix}
\end{equation*}

If we have a set of functions $f_1, f_2, f_3 ...$, that are a solution to a homogeneous function, that set is independent linearly if and only if $\mathbf{W} \neq 0$ for all $x \in I$.

\section{General Solution of a Homogeneous Equation}
Let $y(x)$ be a solution and let $y_1,y_2$ be known solutions to a homogeneous equation $\mr{L(y)}=0$. Suppose on the common interval $I$, $x=t$ where $\mathbf{W}(y_1,y_2) \neq 0$ for all $x=t$. That means $y_1$ and $y_2$ are solutions that can be used to form a superposition, 

\begin{equation*}
	y(x) = c_1y_1 + c_2y_2
\end{equation*}

\section{General Solution of a Non-Homogeneous Equation}
Any function free of arbitrary parameters, that satisfies a non-homogeneous equation is said to be a particular solution of the equation. 
Now if you had a set of solutions, the linear combination of that set and the $y_p$ is also a solution. This means that if you took the solution set from a homogeneous equation, the fundamental solution set for the associated homogeneous equation.

\begin{equation*}
	y(x) = c_1y_1 + c_2y_2 + c_3y_p 
\end{equation*}

\subsection{Reduction of Order}
